Fractional Types

### 2013-02-25 frac.tex
add URL for code

Having introduced the syntax of our extended language, its semantics in the
category of sets and relations, and its operational semantics using forward
and backwards interpreters, we now illustrate its expressiveness as a
higher-order programming language. In the following presentation consisting
of numerous programming examples, we use {{bool}} as an abbreviation of
{{1+1}} with {{true}} as an abbreviation for {{left ()}} and {{false}} as an
abbreviation for {{right ()}}. In addition, instead of presenting the code
using the syntax of {{Pi}}, we use circuit diagrams that are hopefully more
intuitive. Each diagrams represents a combinator whose evaluation consists of
propagating values along the wires.  For the sake of readability, we omit
obvious re-shuffling circuitry and elide trivial unit wires which carry no
information.\footnote{The full code is available upon request. We plan on
  releasing it as soon as possible.}

>>>>

Having introduced the syntax of our extended language, its semantics in the
category of sets and relations, and its operational semantics using forward
and backwards interpreters, we now illustrate its expressiveness as a
higher-order programming language. In the following presentation consisting
of numerous programming examples, we use {{bool}} as an abbreviation of
{{1+1}} with {{true}} as an abbreviation for {{left ()}} and {{false}} as an
abbreviation for {{right ()}}. In addition, instead of presenting the code
using the syntax of {{Pi}}, we use circuit diagrams that are hopefully more
intuitive. Each diagrams represents a combinator whose evaluation consists of
propagating values along the wires.  For the sake of readability, we omit
obvious re-shuffling circuitry and elide trivial unit wires which carry no
information.\footnote{The full code is available at
\url{www.cas.mcmaster.ca/~carette/PiFractional}.}
